---
title: "Marine Networks - Testing Small Network"
author: "L.A.S. - T. M."
output: html_document
---
## Referencias

1. Clauset, A., Shalizi, C. & Newman, M. (2009). Power-Law Distributions in Empirical Data. SIAM Rev., 51, 661–703

## Setup

```{r setup, eval=T,echo=FALSE }
load(".RData")
#simul  <- F # variable to perform or not the simulations


oldcd <-getwd()


require(pander)
require(plyr)
require(dplyr)
panderOptions('table.split.table',Inf)
panderOptions('table.style', 'multiline')
options("scipen"=6, "digits"=4)

#Load package
library(poweRlaw) 
source("R/dist_fun.r")
# 
# Load functions for discrete distributions
# # 
# Load functions for continuous ht distributions
# 

source("R/powerlaw/discpowerexp.R")
source("R/powerlaw/discexp.R")
source("R/powerlaw/zeta.R")
# 
# Load functions for continuous ht distributions
# 
source("R/powerlaw/powerexp.R")
source("R/powerlaw/exp.R")
source("R/powerlaw/pareto.R")
#

```


# Fit degree distribution for total food-web

```{r degreeFitTot, eval=T,echo=F,message=T,warning=T}

dtot <- read.delim("Data/AllNetworksDegree.dat", quote="",stringsAsFactors = F)
unique(dtot$Network)

opt.output <- vector("list", length=0)
opt.output$GOF <- 0
opt.output$ploting <- 1

# Only new networks
#
dtot <- dtot %>% filter(Network=="Peru")

fit <- dtot %>% group_by(Network) %>% do(fit_ht_dplyr_helper(.))
fitML <- bind_rows(fitML,fit)

# Correct negative uniform parameter
#
fitML1 <- fitML %>% filter(ModelNames=="Uniform") %>% mutate(par1=abs(par1))
fitML <- fitML %>% filter(ModelNames!="Uniform") %>% bind_rows(fitML1)
# freq_plot_con_ht(dt$Grado,dft)

fitML1 <- filter(fitML, Delta_AICc==0) %>% mutate_if(is.numeric, round, digits=4) 

write.csv(fitML, file="AllNetworksFit.csv")
write.csv(fitML1, file="AllNetworksLowerAICc.csv")

save.image()

# fitML$xmin<-1
# dt <- filter(dtot, Network=="Jamaica")
# ft <- filter(fitML, Network=="Jamaica")
# 
# cdfplot_displ_exp(dt$Degree,ft)
# freq_plot_con_ht(dt$Degree,ft)
# dtot %>% group_by(Network) %>% do(fit_ht_dplyr_helper(.))


```


# Generate random networks to obtain confidence intervals and compare with experimental FW


```{r ramdomSmallWorld, eval=T,echo=F,message=T,warning=T}
require(igraph)
require(dplyr)
source("R/small_world_fun.r")

# Read networks data
#
ntot <- read.delim("Data/AllNetworksSLC.dat", quote="",stringsAsFactors = F)
unique(ntot$Network)
# Calculate confidence intervals for random networks (erdos.renyi)
#
swtot <- ntot %>% group_by(Network) %>% do( calc_cpl_cc(.$Size,.$Links,.$CPL,.$CC)) %>% inner_join(ntot) 
swtot <- swtot %>% arrange(desc(C))


# Arrange using Connectivity in descending order 
#
xlbl <-swtot %>% arrange(C) 
#
# Add SW test empirical CPL inside random CPL
#             empirical CC > random CC
#
swtot <- swtot %>% mutate(isInsideCPL = ( CPL<=cha.pathUp), isGreaterCC =( CC>clus.coefHigh),
                          isSW= isInsideCPL & isGreaterCC, CPL_ratio=CPL/cha.pathMean, CC_ratio=CC/clus.coefMean,isSWness=SWness>SWnessCI)  

# Plot CC CPL Ratios with colors 
#
require(ggplot2)
require(viridis)
require(cowplot)
ggplot(swtot, aes(CPL_ratio,CC_ratio,shape=isSW,fill=isSW)) + geom_point() + theme_bw()+  scale_colour_viridis(discrete = T) + scale_fill_viridis(discrete = T) + geom_text(aes(label=Network),check_overlap = TRUE,size=3,vjust=0,nudge_y = 0.03) +  theme(legend.position="bottom") + scale_shape_manual(values=c(21,25))+ ylab(expression(CC[Empirical]/CC[Random])) +  xlab(expression(CPL[Empirical]/CPL[Random]))
ggsave("figures/IsSmallWorld_CPL_CC.png",width=5,height=6,units="in",dpi=600)



ggplot(swtot, aes(CPL_ratio,CC_ratio,shape=isSWness,fill=isSWness)) + geom_point() + theme_bw()+  scale_colour_viridis(discrete = T) + scale_fill_viridis(discrete = T) + geom_text(aes(label=Network),check_overlap = TRUE,size=3,vjust=0,nudge_y = 0.03) +  theme(legend.position="bottom") + scale_shape_manual(values=c(21,25))+ ylab(expression(CC[Empirical]/CC[Random])) +  xlab(expression(CPL[Empirical]/CPL[Random]))
ggsave("figures/IsSmallWorld_ness_CPL_CC.png",width=5,height=6,units="in",dpi=600)

##

ggplot(swtot, aes(Network,CC,shape=isSW)) + geom_point() + geom_linerange(aes(ymin = clus.coefLow, ymax = clus.coefHigh)) +theme_bw()+coord_flip() + scale_shape_manual(values=c(21,25),guide=FALSE) + scale_colour_viridis(discrete = T,guide=FALSE)+ scale_x_discrete(limits=xlbl$Network) # + scale_y_log10()  

# Plot in BW Clustering Coeficient
#
A <- ggplot(swtot, aes(Network,CC,shape=isSW)) + geom_point() + geom_errorbar(aes(ymin = clus.coefLow, ymax = clus.coefHigh),width=0.1) +theme_bw()+coord_flip()+ scale_shape_manual(values=c(21,25),guide=FALSE) + scale_x_discrete(limits=xlbl$Network)  + theme(axis.title.y = element_blank())

#ggsave("figures/CC_rnd95confint.png",width=5,height=6,units="in",dpi=600)

# Plot in BW Path Length
#
B <- ggplot(swtot, aes(Network,CPL,shape=isSW)) + geom_point() + geom_errorbar(aes(ymin = cha.pathLow, ymax = cha.pathUp),width=0.1) +theme_bw()+coord_flip()  + scale_x_discrete(limits=xlbl$Network) + scale_shape_manual(values=c(21,25),guide=FALSE) + theme(axis.text.y = element_blank()) + xlab("")
#ggsave("figures/CPL_rnd95confint.png",width=5,height=6,units="in",dpi=600)

plot_grid(A,B,labels = c("A","B"),align = "h",rel_widths = c(1,.8))
ggsave("figures/CC_CPL_rnd95confint.png",width=7,height=6,units="in",dpi=600)

# Save csv file with all parameters and confidence intervals for random networks
#
write.csv(swtot, file="AllNetworksSLC_confint.csv")
save.image()
```


# Calculate count and proportion of basal, intermediate and top predator species

* Do not work well with some networks e.g. Weddell

```{r ramdomSmallWorld, eval=T,echo=F,message=T,warning=T}
require(dplyr)
require(igraph)

a_files <-list.files(path="Data/FoodWebs/",pattern="^.*\\.csv$")
fw_basaltop <- data.frame()

for (i in 1:length(a_files)){

  web <- read.csv(file = paste0("Data/FoodWebs/", a_files[i]), header = T,check.names = F)
  dw <- dim(web)
  if(dw[2]==2 )
  {
    g <- graph_from_adj_list(web)
  } else {
    
    if(dw[1]<dw[2]){
      web <- web[,2:dw[2]]
      dw <- dim(web)
      colnames(web)
    }
    if(dw[1]!=dw[2]) stop(paste("non square",a_files[i]))
  
    g <- graph_from_adjacency_matrix(as.matrix(web))
    V(g)$label <- colnames(web)
  }
  
  calc_topological_indices(g)
  # Number and proportion of vertices with outgoing links = basal species
  bas.count <- length(V(g)[degree(g, mode = 'out') > 0 & degree(g, mode = 'in') == 0])
  bas.prop <- bas.count/vcount(g)
  
  # Number and proportion of vertices with both incoming and outgoing links = intermediate species
  int.count <- length(V(g)[degree(g, mode = 'out') > 0 & degree(g, mode = 'in') > 0])
  int.prop <- int.count/vcount(g)
  
  # Number and proportion of vertices with incoming links = top predators
  top.count <- length(V(g)[degree(g, mode = 'in') > 0 & degree(g, mode = 'out') == 0])
  top.prop <- top.count/vcount(g)
  
  # Proportion of primary producers/consumers 
  # 'Detritus' should be neglected as basal species (bas.count)
  nd <- length(grep("detr", V(g)$label, ignore.case = TRUE, value=F  ))
  
  pp.c <- (bas.count-nd)/(int.count+top.count)
  fw_basaltop <- bind_rows(fw_basaltop,
                           data.frame(Network=strsplit(a_files[i],"_",fixed=T)[[1]][1],basCount=bas.count,basProp=bas.prop,intCount=int.count,intProp=int.prop,topCount=top.count,topProp=top.prop, pcProp=pp.c))

}

require(pander)
panderOptions('table.split.table',Inf)
panderOptions('table.style', 'multiline')

pandoc.table(fw_basaltop)
```
